\large{Vipassana for Hackers} \\ \Huge{The Proposal} \\ \large\textit{Version 0.1}

### 2024-06-27 the-proposal/the-proposal.tex
timeframes, risks, etc... first draft done

\section{STRENGTHS AND WEAKNESSES OF THE STUDY}

@@

* devolves into performance art
* line between science / art is blurry
* forced to take robes
* financially unsustainable

\section{PUBLIC HEALTH SIGNIFICANCE}
\section{BUDGET AND MOTIVATION}
- resources required

\section{Conflict of Interest Statement?}

\section{REFERENCES}
\section{APPENDICES}

@@

It is worth noting that this schedule generally persists across weekends and contains
flexibility for longer or shorter writing periods.
It is also worth noting that this is a sample schedule for the beginning of the study.
As the study progresses, it is expected that the duration of sleep will lessen.

@@

\section*{References}

>>>>

The nominal timeframe for the study will be throughout the course of the
life of the initial researcher-subject (me), and any further subjects
added to the study over time.

Results of the study and experience reports will be sent to sponsors
on a quarterly basis.
Less frequent aggregate results will be published in the form of
papers, articles, and books, with no fixed timeline.

\section{Strengths and Weaknesses of the Study}

The study will provide an in-depth examination of Vipassana meditation
as no other prior study has been able to formulate of any meditation
technique.
The sponsorship model will prevent the study from getting mired in
the examination of narrow outcomes.

As mentioned previously, the study is not structured to provide
significant statistical data out of which other researchers may draw
data-oriented conclusions.

@@

There is a significant risk that such a broad study will devolve into
something of a performative art piece.
Since the writing produced by the study will be inherently subjective,
it will represent a sort of literary art form.
The line between Science and Art under these circumstances is blurry.
Avoiding this degredation of outputs is a primary concern.

There is a more acute risk that, after years of heavy meditation practice,
it will be natural to choose to renounce the householder life and take on
the role of a monk entirely, regardless of what other difficulities that
presents.

There is a final acute risk of financial unsustainability.
If the sponsorship model for the study cannot sustain even one person
financially, it will not be possible to continue with the study
indefinitely.

\section{Public Health Significance}

The significance of the study's outcomes for public health are parallel
to the current accelerating adoption of Vipassana meditation as the
primary meditation technique for many thousands, if not millions, of
householder and monastic practitioners.

If the outcomes of the study are resoundingly positive, it strongly
implies that Vipassana meditation could be an effective tool in
improving public health.
However, if negative effects are detected throughout the course of the
study, it could imply the opposite --- that we should be cautious in
employing Vipassana meditation as a tool for public health improvements.

\section{Budget}

Initially, the resources required to see this study through to completion
will be measured entirely by an individual's annual income.
To reduce the temptation of returning to a career in software development
(which I engaged in previously), that annual income would need to be
comparable to that of an intermediate software developer.
In Canada (where I currently reside), that figure is approximately
\$150,000 - \$200,000 CAD per annum.

As the study progresses, other resources will become a constraint, such as
access to commercial EEG, ECG, and fMRI equipment.
As such, the study will be run through Atapi Research Inc. to separate
study finances from my personal finances.

\section{Conflict of Interest Statement}

There is an inherent conflict of interest produced by the fact that I have
chosen Vipassana meditation as the single meditation technique I will use
for the rest of my life.
However, there is no way around this if the study is to focus on an
individual who has made precisely such a choice.

\section{Appendices}

@@

It is worth noting that this schedule generally persists across weekends and contains
flexibility for longer or shorter writing periods.
It is also worth noting that this is a sample schedule for the beginning of the study.
As the study progresses, it is expected that the duration of sleep will lessen.
Monthly and yearly schedules will include periods of total and partial seclusion,
such as meditation courses (24 hours of meditation per day, less deep sleep cycles)
and meditation retreats (16+ hours of meditation per day).

@@

\newpage

% \section*{References}
